Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-12-31 submission/NatCom_appendix.tex
getting appendix in place
tables updated

\subsection{Supplementary Tables}

@@

@@

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 imagenet-1k  & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & EfficientNet  &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & PreResNet     &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & ShuffleNet    &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & VGG           &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & DLA           &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & HRNet         &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & DRN-C         &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & SqueezeNext   &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & ESPNetv2      &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & IGCV3         &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & SqueezeNet    &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & ProxylessNAS  &  XXX &   XXX &  XXX &  XXX \\
\hline
 cifar-10     & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 cifar-10     & DIA-ResNet    &  XXX &   XXX &  XXX &  XXX \\
 cifar-10     & SENet         &  XXX &   XXX &  XXX &  XXX \\
\hline
 cifar-100    & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 cifar-100    & DIA-ResNet    &  XXX &   XXX &  XXX &  XXX \\
 cifar-100    & SENet         &  XXX &   XXX &  XXX &  XXX \\
 cifar-100    & WRN           &  XXX &   XXX &  XXX &  XXX \\
\hline
 svhn         & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 svhn         & DIA-ResNet    &  XXX &   XXX &  XXX &  XXX \\
 svhn         & SENet         &  XXX &   XXX &  XXX &  XXX \\
 svhn         & WRN           &  XXX &   XXX &  XXX &  XXX \\
 svhn         & ResNeXt       &  XXX &   XXX &  XXX &  XXX \\
\hline
 cub-200-2011 & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 cub-200-2011 & SENet         &  XXX &   XXX &  XXX &  XXX \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{Kendall-$\tau$ results for our analysis of all CV models in Table~\ref{table:datasets}. }
\label{table:KTresults}
\end{table}

\subsection{Supplementary Figures}

@@

>>>>

%%\subsection{Supplementary Tables} 
\subsection{Supplementary Details}

@@

Tables and figures summarizing this analysis (in a more fine-grained way than provided by Table~\ref{table:results}) are presented next.

@@

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
imagenet-1k & ResNet  & 0.77 &  0.74 & 0.88 & 0.88 \\
 imagenet-1k & EfficientNet  & 0.67 &  0.79 & 0.66 & 0.66 \\
 imagenet-1k & PreResNet  & 0.65 &  0.54 & 0.87 & 0.87 \\
 imagenet-1k & ShuffleNet  & 0.39 &  0.09 & 0.85 & 0.82 \\
 imagenet-1k & VGG  & 0.82 &  0.76 & 0.52 & 0.61 \\
 imagenet-1k & DLA  & 0.51 &  0.82 & 0.78 & 0.69 \\
 imagenet-1k & HRNet  & 0.56 &  0.44 & 0.61 & 0.61 \\
 imagenet-1k & DRN-C  & 0.90 &  0.81 & 0.90 & 0.90 \\
 imagenet-1k & SqueezeNext  & 0.47 &  -0.33 & 0.73 & 0.73 \\
 imagenet-1k & ESPNetv2  & 0.00 &  0.80 & 1.00 & 1.00 \\
 imagenet-1k & SqueezeNet  & 0.33 &  0.00 & 0.67 & 0.67 \\
 imagenet-1k & ProxylessNAS  & 0.33 &  0.33 & 0.33 & 0.33 \\
 imagenet-1k & IGCV3  & 1.00 &  0.00 & 1.00 & 1.00 \\
\hline
 cifar-10 & ResNet  & 0.64 &  0.64 & 0.71 & 0.71 \\
 cifar-10 & DIA-ResNet  & 0.79 &  0.50 & 0.86 & 0.79 \\
 cifar-10 & SENet  & 0.74 &  0.95 & 0.95 & 0.95 \\
\hline
 cifar-100 & ResNet  & 0.64 &  0.57 & 0.64 & 0.64 \\
 cifar-100 & DIA-ResNet  & 0.93 &  0.43 & 0.93 & 0.93 \\
 cifar-100 & SENet  & 1.00 &  1.00 & 1.00 & 1.00 \\
 cifar-100 & WRN  & 0.67 &  -0.67 & 0.00 & 0.00 \\
\hline
 svhn & ResNet  & 0.81 &  0.71 & 0.81 & 0.81 \\
 svhn & DIA-ResNet  & 0.86 &  0.86 & 0.57 & 0.57 \\
 svhn & SENet  & 1.00 &  1.00 & 0.67 & 0.67 \\
 svhn & WRN  & -0.33 &  -0.33 & 0.67 & 0.67 \\
 svhn & ResNeXt  & 0.67 &  0.67 & 0.33 & 0.33 \\
\hline
 cub-200-2011 & ResNet  & 1.00 &  1.00 & -0.33 & -0.33 \\
 cub-200-2011 & SENet  & 0.87 &  0.87 & -0.20 & -0.20 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{Kendall-$\tau$ results for our analysis of all CV models in Table~\ref{table:datasets}. }
\label{table:KTresults}
\end{table}

%%\subsection{Supplementary Figures}
\subsection{Supplementary Tables and Figures}

@@

\michael{Probably some discussion of why these metrics are the right ones, e.g., as opposed to $p$ values, to address R1 comments.}
